---
title: "CleanData4"
output: html_document
keep_md: true
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```

Here are the packages I am using
```{r usedLibraries, suppressPackageStartupMessages}
library(dplyr,warn.conflicts = FALSE, quietly=T)
library(quantmod,warn.conflicts = FALSE,quietly=T)
library(lubridate,warn.conflicts = FALSE,quietly=T)
```
## ACS Idaho Housing

Downloading 2006 American Community Survey housing of the ststae of Idaho.
```{r download ACS}
ID2006 ="./ACSIdahoHous2006.csv"
if (!file.exists(ID2006)){
     download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv",ID2006,mode="wb")
}
IDHousing <- read.csv(ID2006,stringsAsFactor=FALSE)
df <-as.data.frame(IDHousing)
Idaho<- tbl_df(df)
Idaho
```
##Q1: 
Apply strsplit() to split all the names of the data frame on the characters "wgtp". The value of the 123 element of the resulting list:
```{r strsplit}
strsplit(names(Idaho),"wgtp")[[123]]
```
##Q2:
GDP data: Load the Gross Domestic Product data for the 190 ranked countries from the World Bank data, and find the average
```{r GDP}
GDPfile ="./GDP.csv"
if (!file.exists(GDPfile)){
     download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv",GDPfile,mode="wb")
}
GDP <- read.csv(GDPfile,stringsAsFactor=FALSE)
df2 <-as.data.frame(GDP)
GDP_df<- tbl_df(df2)
GDP_df = rename(GDP_df,"CountryCode"=X,"Size_Millions_USD"=X.3,"Long.Name"=X.2,"Ranking"=Gross.domestic.product.2012)
GDP_df=select(GDP_df,-(6:10),-3)
names(GDP_df)

GDP_df = filter(GDP_df, CountryCode!=""& Ranking!="")
GDP_df<- mutate(GDP_df,Size_Millions_USD=as.numeric(gsub(",", "", Size_Millions_USD,fixed = TRUE)))
GDP_df
mean(GDP_df$Size_Millions_USD)
```

##Q3: 
Number of countries that start with the word "United"
```{r United}
length(grep("^United",GDP_df$Long.Name))
```

##Q4:  
Education data
```{r education}
edufile ="./edu.csv"
URL2 <-"https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv"
if (!file.exists(edufile)){
      download.file(URL2,edufile,mode="wb")
}
edu <- read.csv(edufile,header=TRUE,stringsAsFactor=FALSE)
df3 <-as.data.frame(edu)
edu_df<- tbl_df(df3)
grep("[Jj]une",edu_df)
## showing that the fiscal year end is in Special.Notes column
length(grep("Fiscal year end: [Jj]une",edu_df$Special.Notes))
grep("[Jj]une",edu_df$Special.Notes,value = T)
```


##Q5:
Using Quantmod package to get historical NASDAQ and NYSE stock prices. Sampling Amazon's stock prices
```{r Amazon,warning=FALSE}
amzn = getSymbols("AMZN",auto.assign=FALSE,"getSymbols.warning4.0"=FALSE)
sampleTimes = index(amzn)
head(sampleTimes)
```
Number of values were collected in 2012? on Mondays in 2012?
```{r dates}
sum(year(ymd(sampleTimes))==2012)
sum(year(ymd(sampleTimes))==2012 & (wday(ymd(sampleTimes))==2))
```

