---
title: "Wk3Q"
output: html_document
keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE, message=FALSE)
```

Here are all the libraries I have used:
```{r libraries, ,suppressPackageStartupMessages()}
library(jpeg); library(dplyr);  
#library(Hmisc)
```

##1. ACS housing data
Loading the data

```{r load_data}
df <-read.csv("ACSIdahoHous2006.csv")
```
The agricultural production column is "AGS" and the land size column is "ACR". From the description in the code-book:

"ACR: Lot size

b N/A (GQ/not a one-family house or mobile home)

1 House on less than one acre

2 House on one to less than ten acres

3 House on ten or more acres

-------------------------------

AGS: Sales of Agriculture Products

b N/A (less than 1 acre/GQ/vacant/2 or more units in structure)

1 None

2 $ 1 - $ 999

3 $ 1000 - $ 2499

4 $ 2500 - $ 4999

5 $ 5000 - $ 9999

6 $10000+"

```{r neededColumns}
df$AGS <- as.factor(df$AGS)
summary(df$AGS)

df[, 'ACR'] <- as.factor(df[, 'ACR'])
summary(df$ACR)
df$agricultureLogical <-(df$ACR==3 & df$AGS ==6)

summary(df$agricultureLogical)
#head(df[which(df$agricultureLogical),])
```

##2. JPG image
```{r JPG}
imgfile="./instructor.jpg"
if(!file.exists(imgfile)){
     download.file("https://d396qusza40orc.cloudfront.net/getdata%2Fjeff.jpg", imgfile, mode = "wb")}
img <-readJPEG(imgfile, native = TRUE)
quantile(img,probs = seq(0, 1, 0.1))
```

##3. GDP and Education DataSets

```{r GDP_EDU}
URL1 <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FGDP.csv"
GDPfile = "./GDP.csv"
if(!file.exists(GDPfile)){
     GDP <-read.csv(URL1, sep=',',strip.white=TRUE,stringsAsFactor=FALSE)
}
URL2 <-"https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv"
EDUfile="./edu.csv"
if(!file.exists(EDUfile)){
     edu <-read.csv(URL2,header=TRUE,stringsAsFactor=FALSE)
}

edu <- as.data.frame(edu)
edu_df <- tbl_df(edu)
#edu_df
GDP <- as.data.frame(GDP)
GDP_df <- tbl_df(GDP)
GDP_df
```
While the education data seems well formatted, the GDP is not.  So let's clean up:
```{r clean_GDP}
#colnames(GDP_df)
GDP_df = rename(GDP_df,"CountryCode"=X,"Size_Millions_USD"=X.3,"Long.Name"=X.2,"Ranking"=Gross.domestic.product.2012)
colnames(GDP_df)
GDP_df=select(GDP_df,-(6:10),-3)

GDP_df$Ranking <-as.numeric(GDP_df$Ranking)

GDP_df<- mutate(GDP_df,Size_Millions_USD=trimws(Size_Millions_USD))
#get rid of the , in the numbers; otherwise NAs
GDP_df<- mutate(GDP_df,Size_Millions_USD=as.numeric(gsub(",", "", Size_Millions_USD,fixed = TRUE)))

summary(GDP_df$Size_Millions_USD)
```
Lots of empty rows at the bottom. I am deleting all the rows where CountryCode is not letters.
```{r MoreEdit}
GDP_df = filter(GDP_df, CountryCode!=""& Ranking!="")
tail(GDP_df,n=15)
```
The data is cleaner now. Let's merge
```{r mergeOrder}
EduGDP<-merge(GDP_df,edu_df,by="CountryCode")
#Order descending GDP rank
EduGDP<- arrange(EduGDP,desc(Ranking))
#tail(EduGDP)
#head(EduGDP,n=15)
```
Make a dataframe for high-income OECD/non-OECD countries
```{r highincome}
by_Income <- group_by(EduGDP,Income.Group)
summarise(by_Income,mean(Ranking))
```

The table for OECD and GDP quantiles
```{r quantile}
#colnames(EduGDP)
EduGDP <- mutate(EduGDP,RankQuant=cut(Ranking,breaks=6)) 
#EduGDP$RankQuant
#library(plyr)

EduGDP%>%filter(Income.Group=="Lower middle income")%>%
          count(RankQuant,sort = TRUE)
#tail(EduGDP%>%count(RankQuant,Income.Group,sort = TRUE),n=15)
EduGDP%>%filter(Income.Group=="Lower middle income")%>%select(CountryCode,RankQuant,Ranking)
```
Looks fine now!